An Improved ANS Transaction Template

### 2018-01-26 paper.tex
adding a table

    Looks at the effective $\theta$ values of the cascade at the third level in both
case

>>>>

\bottomrule
\end{tabular}
  \caption{Cascade effective $\theta$ as a function of the cascade level and the
  case considered.}
  \label{tab:cascade_theta}
\end{table}
As illustrated on Table \ref{tab:cascade_theta} the effecive cut of the the
different level increase up to $0.54$ for the fifth stage on case 2. The high
effecive cut value increase the product production rate but decrease the
enrichment ratio.
